\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Journal 9}
\author{Abdullah Abumouzah }

 \usepackage{url}
 
 
\begin{document}

\maketitle


\begin{itemize}
    \item As long as the AWS, I'm so glad I had the chance to try it.  
    \item I thought I submitted the right registration request at the beginning but I then I noticed that I didn't complete the request because there were two choices to select and I wasn't sure what option should I select.
    
    \item After creating the account I got charged with $75$ Dollar
    \item When first created the instance I selected the free available operating system (Ubuntu Server 14.04 LTS (HVM), SSD Volume Type). 
    
    \item I first wasn't really sure what the assignment requirement is but then I figured it out.
    
    \item After running the instance I had to update the operating system and also install Python into the instance.
    
    \item I used my MacBook Pro to access the instance through the SSH protocol. 
    
    \item to complete the assignment I built a python code that prints my name into a text file
    \item To transfer files from and to the instance and my local machine, I used SCPWin software that allow me to access the instance and make all the transferring. 
    \item This assignment wasn't really tough as all the tools were easy to use and the instruction on the manual Amazon provides is easy to follow.  
    \item For the peer review of my paper, I had some good points that should be implemented on the paper. 
    \item I had some other points I think I will not apply just because I think there are other ways to make the change for example, I don't think I will make a pseudocode on this paper instead I might include a figure that explain the steps in a better way. 
    \item One point I should put more attention toward is the crammer, I think that needs more attention. 

    
    \item You can download this file from github from the below link: \url{https://github.com/aabumouzah/Journal-9}
\end{itemize}


\end{document}
